---
title: "Simple document"
output: github_document
---
```{r}
library(tidyverse)
library(readxl)
library(haven)
```
Let us import the `FAS_litters.csv` csv using a relative path
```{r}
litters_df=
  read_csv("data/FAS_litters.csv")
litters_df
```
```{r}
litters_df=
  janitor::clean_names(litters_df)
litters_df
```
Import the same dataset using an absolute path
```{r}
litters_df_abs=
  read_csv("~/Desktop/P8105/Lecture/data_wrangling/P8105_data_wrangling1/data/FAS_litters.csv")
litters_df_abs=
  janitor::clean_names(litters_df_abs)
litters_df
```
Import pup dataset
```{r}
pups_df=
  read_csv("data/FAS_pups.csv")
pups_df=
  janitor::clean_names(pups_df)
pups_df
```
## Look at data
```{r}
litters_df
head(litters_df)
tail(litters_df)
```
```{r eval=FALSE}
view(litters_df)

```{r}
str(litters_df)
skimr::skim(litters_df)
```
## Option in `read_*`
```{r}
litters_df=
  read_csv("data/FAS_litters.csv", skip=10, col_names = FALSE)
litters_df
```
Look at NA variables
```{r}
litters_df=
  read_csv("data/FAS_litters.csv",na=c("NA",19))
litters_df
```
Column Type
```{r}
litters_df=
  read_csv("data/FAS_litters.csv",col_types = cols(Group=col_factor()))
litters_df
```
## Other file types
Import xlsx file first
```{r}
mlb_df=
  read_excel("data/mlb11.xlsx")
mlb_df
```
Import sas file 
```{r}
pulse_df=read_sas("data/public_pulse_data.sas7bdat")
pulse_df
```


